### 2013-11-01 article2013.Rmd
Changing the data munging into vector algebra
restructuring the whole lot. Creative destruction

% Attributions for Poverty in Post-Socialist Countries[^*]
% Markus Kainu[^**];Mikko Niemelä[^***]
% March 2013

[^*]:*Work in progress. Please, do not cite without permission of authors*

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(knitr)
knit("article2013.Rmd")
system("~/.cabal/bin/pandoc article2013.md --number-sections -o article2013.pdf")
system("~/.cabal/bin/pandoc -s article2013.md --toc --number-sections -o article2013.html")
system("~/.cabal/bin/pandoc -f markdown -t docx article2013.md -o article2013.docx --standalone --toc --number-sections")

@@

lftp -u np16003 -e "mirror -R;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions
```

@@

@@

The respondents were asked the following question which measures public perceptions of the causes of poverty: **In your opinion, what is the main reason why there are some people in need in our country today?**

- Because they have been unlucky
- Because of laziness and lack of willpower
- Because of injustice in our society
- It is an inevitable part of modern life
- Other

@@

```{rtablepredictor, results='asis', echo=FALSE}
Variable <- c("Transfer dependency","Low education","Perceived low income level","Income compared to past","Income compared to future","Effect of financial crises")
Description <- c("Social or private transfers \n as main source of income","No or only compulsory level education","Perceived income level below the country median","Perceived change in income compared to situation in four years ago","Expected change in income over the next four years","Whether respondents perceives that their household has suffered the financial crisis great or fair amount")
table <- data.frame(Variable,Description)
library(xtable)
xtbl <- xtable(table, caption="Individual level predictors")
print.xtable(xtbl, type="latex", comment=FALSE, size="scriptsize",include.rownames=FALSE)
```

@@

@@

[^*****]:R-code for data transformation and analysis is available at [research.muuankarski.org/code/](http://research.muuankarski.org/code/)

Our multilevel modelling focuses first in bivariate connections between two dependent variables and both individual and country level independent variables(See Appendix B). At the second step we include all individual level variables to a single model (models sb1 and ib1). Then we add each of the four country level variables one at the time (models sb2/ib2 - sb5/ib5). With limited number of countries we are obliged to use only few contextual variables. Tables will include both a fixed effects and a random effects part. The fixed effects part will include odds ratios and statistical significances of independent variables, while the random effects part will indicate the country-level variance and standard deviation, deviance and number of cases and groups. Full model summaries currently available at [research.muuankarski.org/code/](http://research.muuankarski.org/code/).

@@

@@

![Change in total GDP in 2007 - 2010 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gdp.png)

@@

![Gini coefficient and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gini.png)

@@

![World Bank's Voice and Accountability index in 2011 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_wbgi.png)

@@

- click for tables: [code/multilevel_models.pdf](code/multilevel_models.pdf)
- click for RC19 tables: [code/multilevel_modelsRC19.pdf](code/multilevel_modelsRC19.pdf)

>As the main controbution of our study relates to cross-national variation of attributions for poverty within post-socialist countries, we shall largely focus on the effects of contextual variables. Nevertheless, as we are covering several countries that haven't been included in previous studies of individual level determinants, we shall also look carefully at the individual level.

>>>>

% Attributions for Poverty in Post-Socialist Countries[^*]
% Markus Kainu[^**];Mikko Niemelä[^***]
% October 2013

[^*]:*Work in progress

@@

```{roptsattribArticle, echo=FALSE}
opts_chunk$set(echo=FALSE,eval=TRUE,cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=12)
```

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(knitr)
knit("article2013.Rmd")
system("~/.cabal/bin/pandoc article2013.md --number-sections -o article2013.pdf")
system("~/.cabal/bin/pandoc -s article2013.md --toc --number-sections -o article2013.html")
system("~/.cabal/bin/pandoc -f markdown -t docx article2013.md -o article2013.docx --standalone --toc --number-sections")
system("~/.cabal/bin/pandoc article2013.md -o article2013.epub --standalone --toc --number-sections")

@@

```

**Nootti**

*Paperi on vielä hieman vaiheessa ja suosittelen tutustumaan tutkimuksen analytiikkaan osoitteessa: [http://research.muuankarski.org/attributions/](http://research.muuankarski.org/attributions/). Yritän parhaillaan saada monitasomallintamista paremmalle tolalle. Paperissa olevat mallit ovat alustavia ja pitävät sisällään sekä teoreettista että menetelmällistä epätarkkuutta.*

****

@@

![Countries used in the analysis](figure/mapplot.png)

@@

The respondents were asked the following question which measures public perceptions of the causes of poverty: **In your opinion, what is the main reason why there are some people in need in our country today?** (Variable `q309` in LiTS-data)

- Because they have been unlucky
- Because of laziness and lack of willpower
- Because of injustice in our society
- It is an inevitable part of modern life
- Don't know
- Not stated

@@

Table: Individual level predictors

-----------------------------------------------------------------------------
Variable                    Description
------------------------    -------------------------------------------------
Transfer dependency         Social or private transfers as main source of income

Low education               No or only compulsory level education

Perceived low income level  Perceived income level below the country median

Income compared to past     Perceived change in income compared to situation in four years ago

Income compared to future   Expected change in income over the next four years

Effect of financial crises  Whether respondents perceives that their household has suffered the financial crisis great or fair amount
-----------------------------------------------------------------------------

@@

Table: Contextual level predictors

-----------------------------------------------------------------------------
Variable                          Description
------------------------          -------------------------------------------------
Ghange in total GDP 2007 – 2010   Relative change from 2007 to 2010

Gini coefficient                  Measures the distribution of income or consumption expenditure among individuals or households

Voice and Accountability          Indicators measuring the political process, civil liberties and political rights. These indicators measure the extent to which citizens of a country are able to participate in the selection of governments. Indicators measuring the independence of the media is also included.
Description
-----------------------------------------------------------------------------

@@

[^*****]:R-code for data transformation and analysis is available at [http://research.muuankarski.org/attributions/](http://research.muuankarski.org/attributions/)

Our multilevel modelling focuses first in bivariate connections between two dependent variables and both individual and country level independent variables(See Appendix B). At the second step we include all individual level variables to a single model (models sb1 and ib1). Then we add each of the four country level variables one at the time (models sb2/ib2 - sb5/ib5). With limited number of countries we are obliged to use only few contextual variables. Tables will include both a fixed effects and a random effects part. The fixed effects part will include odds ratios and statistical significances of independent variables, while the random effects part will indicate the country-level variance and standard deviation, deviance and number of cases and groups. Full model summaries currently available at [http://research.muuankarski.org/attributions/](http://research.muuankarski.org/attributions/).

@@

```{rattribArticleDescTbl1, results='asis'}
source("code/dv_tables.R")
print.xtable(xtable(tbl5, 
                    caption="Weighted population shares of dependent variable by country",),
              type="latex",
              comment=FALSE, 
              include.rownames=FALSE,
             caption.placement="top")

```

@@

![Change in total GDP in 2007 - 2010 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gdp.pdf)

@@

![Gini coefficient and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gini.pdf)

@@

![World Bank's Voice and Accountability index in 2011 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_wbgi.pdf)

@@

*There we some issues in converts regression outputs so the tables are evolving and can be browsed at: [http://research.muuankarski.org/attributions/code/multilevel_models.html](http://research.muuankarski.org/attributions/code/multilevel_models.html)*

****

```{rattribArticleMultilevel1,results='asis', eval=FALSE}
source("~/workspace/lits/attrib/attrib_year2013/code/multi_logit.R")
library(texreg)
texreg(list(soc.0,
       soc.1,
       soc.2,
       soc.3,
       soc.4),
       use.package=FALSE,
       include.pvalues=TRUE,
       ci.test=NULL,

          caption="Logistic multilevel random intercept model for social blame type of explanation.", caption.above=TRUE, doctype = FALSE,
        custom.coef.names=c("Intercept",
                             "Transfer dependency (Not dependent)",
                             "Education (No education)",
                             "Perceived income (Low)",
                             "Perceived change in income compared to four years ago (Has worsened)",
                             "Expected change in income over next four years (Will worsen)",
                             "Effect of financial crisis (Suffered great or fair amount)",
                             "gini coefficient",
                             "GDP change 2007-2010",
                             "Voice And Accountability (WB)"),
        custom.model.names=c("empty","Model SB1","Model SB2",
                             "Model SB3","Model SB4"))

```

```{rattribArticleMultilevel2, results='asis', eval=FALSE}

texreg(list(ind.0,
          ind.1,
          ind.2,
          ind.3,
          ind.4),
       use.packages=FALSE,
       include.pvalues=TRUE,
       ci.test=NULL,
       caption="Logistic multilevel random intercept model for individual blame type of explanation.", 
       caption.above=TRUE, 
        doctype = FALSE,
                custom.coef.names=c("Intercept",
                             "Transfer dependency (Not dependent)",
                             "Education (No education)",
                             "Perceived income (Low)",
                             "Perceived change in income compared to four years ago (Has worsened)",
                             "Expected change in income over next four years (Will worsen)",
                             "Effect of financial crisis (Suffered great or fair amount)",
                             "gini coefficient",
                             "GDP change 2007-2010",
                             "Voice And Accountability (WB)"),
        custom.model.names=c("empty","Model IB1","Model IB2",
                             "Model IB3","Model IB4"))
```

<!--

As the main controbution of our study relates to cross-national variation of attributions for poverty within post-socialist countries, we shall largely focus on the effects of contextual variables. Nevertheless, as we are covering several countries that haven't been included in previous studies of individual level determinants, we shall also look carefully at the individual level.

-->

### 2013-11-01 descriptive_analysis.Rmd
restructuring the whole lot. Creative destruction

% Descriptive analysis

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(kaRski)
knitpandoc("descriptive_analysis")
```

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=12)
```

@@

```{rdescplot1_1, fig.width=15}
load("~/workspace/lits/attrib/attrib_year2013/data/lits.RData")
library(ggplot2)
library(reshape2)

df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$q227),1)*100)
reg <- as.data.frame(table(df$cntry,df$group))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")

@@

```{rdescplot1_2, fig.width=15}
df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$income),1)*100)
reg <- as.data.frame(table(df$cntry,df$group))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")
x$cond <- factor(x$cond, levels=c("Low","High"))

@@

```{rdescplot2_1, fig.width=15}
df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$q226m_txt),1)*100)
reg <- as.data.frame(table(df$cntry,df$group))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")

@@

```{rdescplot2_2, fig.width=15}

df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$incsour3),1)*100)
reg <- as.data.frame(table(df$cntry,df$group))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")
x$cond <- factor(x$cond, levels=c("Dependent","Not.dependent"))

@@

```{rdescplot3_1, fig.width=15}
df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$q228),1)*100)
reg <- as.data.frame(table(df$cntry,df$group))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")

@@

```{rdescplot3_2, fig.width=15}

tbl <- data.frame(prop.table(table(df$cntry,df$past),1)*100)
reg <- as.data.frame(table(df$cntry,df$group))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")
x$cond <- factor(x$cond, levels=c("same or better","worse"))

@@

```{rdescplot4_1, fig.width=15}
df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$q229),1)*100)
reg <- as.data.frame(table(df$cntry,df$group))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")

@@

```{rdescplot4_2, fig.width=15}

tbl <- data.frame(prop.table(table(df$cntry,df$future),1)*100)
reg <- as.data.frame(table(df$cntry,df$group))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")
x$cond <- factor(x$cond, levels=c("same or better","worse"))

@@

```{rdescplot5_1, fig.width=15}
df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$q515),1)*100)
reg <- as.data.frame(table(df$cntry,df$group))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")

@@

```{rdescplot5_2, fig.width=15}

tbl <- data.frame(prop.table(table(df$cntry,df$edu2),1)*100)
reg <- as.data.frame(table(df$cntry,df$group))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")
x$cond <- factor(x$cond, levels=c("no or compulsory","higher"))

@@

```{rdescplot6_1, fig.width=15}
df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$q801),1)*100)
reg <- as.data.frame(table(df$cntry,df$group))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")

@@

```{rdescplot6_2, fig.width=15}

tbl <- data.frame(prop.table(table(df$cntry,df$crise),1)*100)
reg <- as.data.frame(table(df$cntry,df$group))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")
x$cond <- factor(x$cond, levels=c("Little or not at all","Great or fair amount"))

@@

```{rdescplot7, fig.width=15}
df <- macro[with(macro, order(uw.gini)), ]
df$cntry <- factor(df$cntry, levels=df$cntry)
ggplot(df, aes(x=cntry,y=uw.gini, colour=group)) +
  geom_point(size=5) +
  labs(title="gini coeficient") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

```{rdescplot8, fig.width=15}
df <- macro[with(macro, order(gdpchange07.10)), ]
df$cntry <- factor(df$cntry, levels=df$cntry)
ggplot(df, aes(x=cntry,y=gdpchange07.10, colour=group)) +
  geom_point(size=5) +
  labs(title="gdp change 2007 - 2010") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

```{rdescplot9, fig.width=15}
df <- macro[with(macro, order(wbgi.vae)), ]
df$cntry <- factor(df$cntry, levels=df$cntry)

ggplot(df, aes(x=cntry,y=wbgi.vae, colour=group)) +
  geom_point(size=5) +
    labs(title="Voice and accountability") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

```{rdescplot10, fig.width=15}
library(GGally)
ggpairs(macro[, c("uw.gini", "gdpchange07.10", "wbgi.vae","social.blame","individual.blame")])

@@

# Final plots

![Change in total GDP in 2007 - 2010 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gdp.png)

![Gini coefficient and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gini.png)

![World Bank's Voice and Accountability index in 2011 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_wbgi.png)

>>>>

% Descriptive visualizations

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(kaRski)
knit("descriptive_analysis.Rmd")
system("pandoc -s descriptive_analysis.md -o descriptive_analysis.html --toc --number-section")

knitpandoc("descriptive_analysis",toc)
```

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=10)
```

@@

```{rdescplot1_1}
load("~/workspace/lits/attrib/attrib_year2013/data/lits.RData")
library(ggplot2)
library(reshape2)

df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$q227),1)*100)
reg <- as.data.frame(table(df$cntry,df$group_general))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")

@@

```{rdescplot1_2}
df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$income),1)*100)
reg <- as.data.frame(table(df$cntry,df$group_general))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")
x$cond <- factor(x$cond, levels=c("Low","High"))

@@

```{rdescplot2_1}
df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$q226m),1)*100)
reg <- as.data.frame(table(df$cntry,df$group_general))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")

@@

```{rdescplot2_2}

df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$incsour3),1)*100)
reg <- as.data.frame(table(df$cntry,df$group_general))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")
x$cond <- factor(x$cond, levels=c("Dependent","Not.dependent"))

@@

```{rdescplot3_1}
df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$q228),1)*100)
reg <- as.data.frame(table(df$cntry,df$group_general))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")

@@

```{rdescplot3_2}

tbl <- data.frame(prop.table(table(df$cntry,df$past),1)*100)
reg <- as.data.frame(table(df$cntry,df$group_general))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")
x$cond <- factor(x$cond, levels=c("same or better","worse"))

@@

```{rdescplot4_1}
df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$q229),1)*100)
reg <- as.data.frame(table(df$cntry,df$group_general))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")

@@

```{rdescplot4_2}

tbl <- data.frame(prop.table(table(df$cntry,df$future),1)*100)
reg <- as.data.frame(table(df$cntry,df$group_general))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")
x$cond <- factor(x$cond, levels=c("same or better","worse"))

@@

```{rdescplot5_1}
df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$q515),1)*100)
reg <- as.data.frame(table(df$cntry,df$group_general))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")

@@

```{rdescplot5_2}

tbl <- data.frame(prop.table(table(df$cntry,df$edu2),1)*100)
reg <- as.data.frame(table(df$cntry,df$group_general))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")
x$cond <- factor(x$cond, levels=c("no or compulsory","higher"))

@@

```{rdescplot6_1}
df$cntry <- factor(df$cntry)
tbl <- data.frame(prop.table(table(df$cntry,df$q801),1)*100)
reg <- as.data.frame(table(df$cntry,df$group_general))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")

@@

```{rdescplot6_2}

tbl <- data.frame(prop.table(table(df$cntry,df$crise),1)*100)
reg <- as.data.frame(table(df$cntry,df$group_general))
reg <- subset(reg, Freq > 0)
reg <- reg[with(reg, order(Var2)), ]
x <- merge(tbl,reg[,1:2],by="Var1")
names(x) <- c("cntry","cond","freq","group")
x$cond <- factor(x$cond, levels=c("Little or not at all","Great or fair amount"))

@@

```{rdescplot7}
df <- macro[with(macro, order(uw_gini)), ]
df$cntry <- factor(df$cntry, levels=df$cntry)
ggplot(df, aes(x=cntry,y=uw_gini, colour=group)) +
  geom_point(size=5) +
  labs(title="gini coeficient") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

```{rdescplot8}
df <- macro[with(macro, order(gdpchange07.10)), ]
df$cntry <- factor(df$cntry, levels=df$cntry)
ggplot(df, aes(x=cntry,y=gdpchange07.10, colour=group)) +
  geom_point(size=5) +
  labs(title="gdp change 2007 - 2010") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

```{rdescplot9}
df <- macro[with(macro, order(wbgi_vae)), ]
df$cntry <- factor(df$cntry, levels=df$cntry)

ggplot(df, aes(x=cntry,y=wbgi_vae, colour=group)) +
  geom_point(size=5) +
    labs(title="Voice and accountability") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

```{rdescplot10}
library(GGally)
ggpairs(macro[, c("uw_gini", "gdpchange07.10", "wbgi_vae","socialBlame","individualBlame")])

@@

# Dependent variable
